\documentclass[titlepage]{scrartcl}
\usepackage{enumitem}
\usepackage[british]{babel}
\usepackage[style=apa, backend=biber]{biblatex}
\DeclareLanguageMapping{british}{british-apa}
\usepackage{url}
\usepackage{float}
\restylefloat{table}
\usepackage{perpage}
\MakePerPage{footnote}
\usepackage{abstract}
\usepackage{graphicx}
% Create hyperlinks in bibliography
\usepackage{hyperref}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\setkomafont{disposition}{\normalfont\bfseries}

\usepackage{blindtext}
\setkomafont{disposition}{\normalfont\fontsize{12}{17}\bfseries}
\setkomafont{section}{\normalfont\fontsize{12}{17}\bfseries}
\setkomafont{subsection}{\normalfont\fontsize{12}{17}\itshape}
\setkomafont{subsubsection}{\normalfont\fontsize{12}{17}\itshape}

\graphicspath{{./resources/}}
\addbibresource{~/Documents/library.bib}

\usepackage{etoolbox}
\makeatletter
\makeatother

\DeclareCiteCommand{\citeyearpar}
    {}
    {\mkbibparens{\bibhyperref{\printdate}}}
    {\multicitedelim}
    {}


\begin{document}
    \title{ECS742\\Interactive Digital Media Techniques\\Assignment 2: Processing Game}
    \subtitle{\LARGE{Report}}
    \author{Sam Perry\\Student Number: 160842984}
    \date{}

    \maketitle


    \section*{Procedure}
    Following instructions provided to create the initial game was a relatively
    straight forward task, given previous experience in programming. The most
    prominent problem was an array indexing error that occured when the
    projectile left the screen. This was quickly fixed by adding conditions to
    check if the projectile was on screen before attempting to access the
    groundLevel array.\\


    On completion of this, a number of further features were implemented to
    build on the basic game. These included adding graphics to the background
    (and other aesthetic changes), generating more detailed maps at random, and
    adding a blast radius to projectiles when coliding with objects.

    \section*{Findings}
    It was observed that a number of DSP related techniques applied to
    animations and content generation in this project.
    For example, the generation of custom terrain was implemented by summing
    sine waves of randomly varying amplitudes and phases. This generated hills
    and valleys randomly (within pre-determined limits) to create a different
    user experience for every game. Collision detection is also dependant on
    sampling theory. For example, is fired directly from one tank to the other,
    but the velocity is so high that it will cover over the width of the tank
    in one frame, the projectile will appear to pass straight through the
    target tank.\\

    The other main features involved expanding on code that had been written
    for previous tasks. for example, creating growing blast radiuses involved
    checking for a collision with an object (such as the ground or a tank),
    increasing the size of the object on each iteration, then checking for
    collisions between the object and a tank.\\
    
    The main difficulty, although rather minor, lied in adjusting to the Java
    language. As familiar concepts such as passing variables by reference do
    not exist in the language, learning the ``Java/Processing way'' of
    implementing features was the main skill aquired in this project.\\

    There are many further improvments that could be implemented in this
    project. However, it would be of great benefit to refactor a large amount
    of the code to take advantage of programming models such as OOP. This would
    allow for quicker and less ``hacky'' implementations of features and would
    improve overall code quality.
    \printbibliography
\end{document}
